Applications of limited information strategies in Menger's game

### 2016-11-30 articles/applications-of-limited-information-strategies-in-mengers-game/article.tex
finish revisions

@@

\author{Steven Clontz}
\address{Department of Mathematics and Statistics, UNC Charlotte,
Charlotte, NC 28262}
\email{steven.clontz@gmail.edu}
\urladdr{stevenclontz.com}

@@

\begin{abstract}
  As shown by Telgarsky and Scheepers,
  winning strategies in the Menger game characterize
  \(\sigma\)-compactness amongst metrizable spaces. This is improved
  by showing that winning Markov strategies in the Menger game
  characterize \(\sigma\)-compactness amongst
  regular spaces, and that winning strategies may be improved to winning
  Markov strategies in second-countable spaces.
  An investigation of
  \(2\)-Markov strategies introduces a new topological property between
  \(\sigma\)-compact and Menger spaces.
\end{abstract}

@@

\begin{figure}[ht]
\begin{center}
\begin{tikzpicture}[x=0.8in,y=0.5in]
% \node at (-3.5,2) {\(\alcompS\kappa\)};
\node at (-3.5,0) {\(\pl F \ktactwin{(k+1)}\schFillStrictGame\kappa\)};
% \node at (0,2) {\(\alcompSP\kappa\)};
\node at (-1.1,1) {\(\pl F \kmarkwin{(k+1)}\menGame{\onePtLind\kappa}\)};
\node at (0,1) {\(\Leftrightarrow\)};
\node at (1,1) {\(\pl F \kmarkwin{(k+1)}\schFillIntGame\kappa\)};
\node at (-1,0) {\(\pl F \kmarkwin{(k+1)}\schFillInitialGame\kappa\)};
\node at (0,0) {\(\Leftrightarrow\)};
\node at (1,0) {\(\pl F \kmarkwin{(k+1)}\schFillGame\kappa\)};
\node at (0,-1) {\(\pl F \kmarkwin{(k+1)}\schFillStrictGame\kappa\)};
% \draw[-implies,double equal sign distance] (-3.2,2) -- (-0.3,2);
\draw[-implies,double equal sign distance] (-2.5,0) -- (-2,0);
% \draw[-implies,double equal sign distance] (-3.5,1.65) -- (-3.5,0.35);
% \draw[-implies,double equal sign distance] (0,1.65) -- (0,1.35);
\draw[-implies,double equal sign distance] (0,0.65) -- (0,0.35);
\draw[-implies,double equal sign distance] (0,-0.35) -- (0,-0.65);
\end{tikzpicture}
\end{center}
\caption{Diagram of Scheeper/Menger game implications}% with \(\alcompS{\kappa},\alcompS{\kappa}\)}
\label{GamesDiagram}
\end{figure}

@@

\begin{proof}
  For \(\alcompS{\omega_1}\), consider the construction of an Aronzajn tree
  as in \cite{MR597342}; this of course
  implies \(\alcompS{\mf c}\) under \(CH\).
  \(\neg\alcompS{\mf c^+}\) is shown by a cardinality argument
  in \cite{MR1129143}.
  The consistency result under \(ZFC+\neg CH\)
  is a lemma for the main theorem in \cite{MR1129143}.
\end{proof}

\begin{figure}[ht]
\begin{center}
\begin{tikzpicture}[x=0.8in,y=0.5in]
\node at (-3.5,1) {\(\alcompS\kappa\)};
\node at (-3.5,0) {\(\pl F \ktactwin2\schFillStrictGame\kappa\)};
% \node at (0,2) {\(\alcompSP\kappa\)};
\node at (-1,1) {\(\pl F \kmarkwin2\menGame{\onePtLind\kappa}\)};
\node at (0,1) {\(\Leftrightarrow\)};
\node at (1,1) {\(\pl F \kmarkwin2\schFillIntGame\kappa\)};
\node at (-1,0) {\(\pl F \kmarkwin2\schFillInitialGame\kappa\)};
\node at (0,0) {\(\Leftrightarrow\)};
\node at (1,0) {\(\pl F \kmarkwin2\schFillGame\kappa\)};
\node at (0,-1) {\(\pl F \kmarkwin2\schFillStrictGame\kappa\)};
\draw[-implies,double equal sign distance] (-3.2,1) -- (-1.9,1);
\draw[-implies,double equal sign distance] (-2.6,0) -- (-1.9,0);
\draw[-implies,double equal sign distance] (-3.5,0.65) -- (-3.5,0.35);
% \draw[-implies,double equal sign distance] (0,1.65) -- (0,1.35);
\draw[-implies,double equal sign distance] (0,0.65) -- (0,0.35);
\draw[-implies,double equal sign distance] (0,-0.35) -- (0,-0.65);
\end{tikzpicture}
\end{center}
\caption{Diagram of Scheeper/Menger game implications}% with \(\alcompS{\kappa},\alcompS{\kappa}\)}
\label{GamesDiagram2}
\end{figure}

@@

\begin{proof}
  Since \(\alcompS\kappa\Rightarrow\pl F \ktactwin2\schFillStrictGame\kappa\) was
  a main result of \cite{MR1129143}, it is sufficient to show that
  \(\alcompS\kappa\Rightarrow \pl F \kmarkwin2\schFillIntGame\kappa\).

  Let \(f_A\) for \(A\in[\kappa]^{\leq\omega}\) witness \(\alcompS\kappa\). We define
  the \(2\)-mark \(\sigma\) as follows:
    \[
      \sigma(\<A\>,0) = \{\alpha\in A: f_A(\alpha) \leq 0 \}
    \]
    \[
      \sigma(\<A,B\>,n+1)
        =
      \{
        \alpha \in A\cap B
      :
        f_B(\alpha) \leq n+1 \text{ or }
        f_A(\alpha)\not=f_B(\alpha)
      \}
    .\]
  For any attack \(\<A_0,A_1,\dots\>\) by \(\pl C\) and
  \(\alpha\in\bigcap_{n<\omega}A_n\), either \(f_{A_n}(\alpha)\) is constant for
  all \(n\), or \(f_{A_n}(\alpha)\not=f_{A_{n+1}}(\alpha)\) for some \(n\);
  either way, \(\alpha\) is covered.
\end{proof}

\begin{corollary}
  \(\pl F \kmarkwin2\menGame{\onePtLind\omega_1}\).
\end{corollary}

@@

\begin{figure}[h]
\begin{center}
\begin{tikzpicture}
  \matrix (m) [matrix of math nodes,row sep=3em,column sep=1em,minimum width=2em]
  {
     \pl F \markwin \menGame{X} &
     \pl F \kmarkwin2 \menGame{X} &
     \pl F \win \menGame{X} &
     \pl C \notwin \menGame{X} \\

     \text{Markov Menger} &
     2\text{-Markov Menger} &
     \text{Strategic Menger} &
     \text{Menger} \\
  };

  \draw[implies-implies,double equal sign distance]
    (m-1-1) -- (m-2-1);
  \draw[implies-implies,double equal sign distance]
    (m-1-2) -- (m-2-2);
  \draw[implies-implies,double equal sign distance]
    (m-1-3) -- (m-2-3);
  \draw[implies-implies,double equal sign distance]
    (m-1-4) -- (m-2-4);

  \draw[-implies,double equal sign distance]
    (m-1-1) -- (m-1-2);
  \draw[-implies,double equal sign distance]
    (m-2-1) -- (m-2-2);
  \draw[-implies,double equal sign distance]
    (m-1-2) -- (m-1-3);
  \draw[-implies,double equal sign distance]
    (m-2-2) -- (m-2-3);
  \draw[-implies,double equal sign distance]
    (m-1-3) -- (m-1-4);
  \draw[-implies,double equal sign distance]
    (m-2-3) -- (m-2-4);

  \draw[-implies,double equal sign distance,bend right=30]
    (m-1-2) -- node {\( \not \)} (m-1-1);
  \path[>=latex,->,bend right=30, dotted]
    (m-2-2) edge node {\( \not \)} (m-2-1)
    (m-1-4) edge node {\( \not \)} (m-1-3)
    (m-2-4) edge node {\( \not \)} (m-2-3);
  \path[>=latex,->,bend right=30, dotted]
    (m-1-3) edge node {\( ? \)} (m-1-2)
    (m-2-3) edge node {\( ? \)} (m-2-2);
\end{tikzpicture}
\end{center}
\caption{Diagram of covering properties related to the Menger game TODO FIX}
\label{menSpec}
\end{figure}

Limited information strategies for the Menger game naturally define a spectrum
of covering properties, see Figure \ref{menSpec}. However,
we do not know if the middle two properties are actually distinct.

@@

We are also interested in non-game-theoretic characterizations of these
covering properties. It has been known for some time that metrizable strategic
Menger spaces are exactly the metrizable \(\sigma\)-compact spaces, shown first
by Telgarksy in \cite{MR753073} and later directly by Scheepers in
\cite{MR1273523}. It's Scheepers' technique which gives inspiration to
the following.

@@

  Let \(\mc U=\{U_\alpha:\alpha<\kappa\}\) be an
  open cover of \(\text{cl}_X(Y)\); for \(y\in Y\), apply regularity to get
  \(V_\alpha\subseteq\text{cl}_X(V_\alpha)\subseteq U_\alpha\)
  with \(V_\alpha\) open.
  Use relative compactness to obtain a finite subcollection of
  \(\{X\setminus\text{cl}_X(Y)\}\cup\{V_\alpha:\alpha<\kappa\}\)
  covering \(Y\): \(\{V_{\alpha_i}:i<n\}\). Then since
  \(\bigcup\{\text{cl}_X(V_{\alpha_i}):i<n\}\) is a closed set in \(X\)
  containing \(Y\), it contains \(\text{cl}_X(Y)\), and thus
  \(\{U_{\alpha_i}:i<n\}\) is a finite subcollection of \(\mc U\) covering
  \(\text{cl}_X(Y)\).

@@

  So if \(\mc U_t\) is a basic open cover for \(t<s\in\omega^{<\omega}\), and
  \(\mc V\) is any basic open cover, we may choose a finite subcollection
  \(\mc F(s,\mc V)\) of \(\mc V\) such that
  \[
    \sigma(\<\mc U_{s\rest 1},\dots,\mc U_{s},\mc V\>)
      \subseteq
    \bigcup \mc F(s,\mc V)
  .\]

@@

\begin{proof}
  If \(X=\bigcup_{n<\omega}R_n\), then for all \(\mc U\), let \(r_{\mc U}(x)\) be the
  least \(n\) such that \(x\in R_n\). Then \(c(\mc V,n)=\bigcup_{m\leq n}R_m\) and
  \(p(\mc U,\mc V) = \emptyset\).
\end{proof}

@@

We may also consider common counterexamples which are finer
than the usual Euclidean line.

@@

\begin{proof}
  Compact sets in \(R_{\mathbb Q}\) cannot contain open intervals,
  and thus are nowhere dense in nonmeager \(\mathbb R\),
  so \(R_{\mathbb Q}\) is not \(\sigma\)-compact. The usual base of
  intervals with rational endpoints (with or without rationals removed)
  witnesses second-countability, and \([-n,n]\) is relatively compact.
\end{proof}

@@

@@

\begin{proof}
  If \(S\supseteq\{s_n:n<\omega\}\) for \(s_n\)
  discrete, then \(U_m=R_\omega\setminus\{s_n:m<n<\omega\}\) yields an
  infinite cover \(\{U_m:m<\omega\}\) with no finite subcollection covering \(S\),
  showing that all relatively compact sets are finite, and \(R_\omega\) is not
  \(\sigma\)-relatively-compact.

  Define the winning strategy \(\sigma\) for \(\pl F\) in \(\menGame{R_\omega}\) as
  follows: let \(\sigma(\<\mc{U}_0,\dots,\mc{U}_{2n}\>)=[-n,n]\setminus C_n\)
  for some countable \(C_n=\{c_{n,m}: m<\omega\}\),
  and let \(\sigma(\<\mc{U}_0,\dots,\mc{U}_{2n+1}\>)=\{c_{i,j} : i,j < n\}\).
\end{proof}

@@

\begin{proof}
  It's sufficient to show that \([0,1]\subseteq R_\omega\) is relatively
  robustly Menger. Let \(f_A\) witness \(\alcompS{\mf c}\)
  for \(A\in[[a,b]]^{\leq\omega}\).
  For each open cover \(\mc U\), let \(A_{\mc U}\) be
  such that \([0,1]\setminus A_{\mc U}\) is \(\mc U\)-finite.
  Let \(r_{\mc U}(x)=0\) if \(x\in[0,1]\setminus A_{\mc U}\) and
  \(r_{\mc U}(x)=f_{\mc A_{\mc U}}(x)\) otherwise.

>>>>

\usepackage{tikz-cd}
\usetikzlibrary{decorations.markings}
\tikzset{not/.style={
  decoration={markings,
    mark= at position 0.5 with {
      \node[transform shape] (tempnode) {$\backslash$};
    }
  },
  postaction={decorate}
}}
\tikzset{maybe/.style={
  color=gray,
  decoration={markings,
    mark=at position 0.5 with {
      \node[color=black] (tempnode) {$?$};
    }
  },
  postaction={decorate}
}}

@@

\author{Steven Clontz}
\address{Department of Mathematics and Statistics, University of South Alabama,
Mobile, AL 36688}
\email{sclontz@southalabama.edu}
\urladdr{clontz.org}

@@

\begin{abstract}
  As shown by Telg\'arsky and Scheepers,
  winning strategies in the Menger game characterize
  \(\sigma\)-compactness amongst metrizable spaces. This is improved
  by showing that winning Markov strategies in the Menger game
  characterize \(\sigma\)-compactness amongst
  regular spaces, and that winning strategies may be improved to winning
  Markov strategies in second-countable spaces.
  An investigation of
  \(2\)-Markov strategies introduces a new topological property between
  \(\sigma\)-compact and Menger spaces.
\end{abstract}

@@

\begin{figure}[ht]
\begin{center}
\begin{tikzcd}[arrows=Rightarrow]
  &
  \pl F \kmarkwin{k+1} \menGame{\onePtLind\kappa}
  \Leftrightarrow
  \pl F \kmarkwin{k+1} \schFillIntGame{\kappa}
    \arrow[d] \\
  \pl F \ktactwin{k+1} \schFillStrictGame{\kappa}
    \arrow[r] &
  \pl F \kmarkwin{k+1}\schFillGame{\kappa}
  \Leftrightarrow
  \pl F \kmarkwin{k+1} \schFillInitialGame{\kappa}
      \arrow[d] \\
  &
  \pl F \kmarkwin{k+1} \schFillStrictGame{\kappa}
\end{tikzcd}
\end{center}
\caption{Diagram of Scheeper/Menger game implications}
\label{GamesDiagram}
\end{figure}

@@

\begin{proof}
  The construction of an Aronzajn tree in \cite[Theorem 5.9]{MR597342}
  produced a witness for \(\alcompS{\omega_1}\); this of course
  implies \(\alcompS{\mf c}\) under \(CH\).
  \(\neg\alcompS{\mf c^+}\) is shown by a cardinality argument
  in \cite{MR1129143}.
  The consistency result under \(ZFC+\neg CH\)
  is a lemma for the main theorem in \cite{MR1129143}.
\end{proof}

\begin{figure}[ht]
\begin{tikzcd}[arrows=Rightarrow]
  \alcompS\kappa
    \arrow[r]
    \arrow[d] &
  \pl F \kmarkwin2 \menGame{\onePtLind\kappa}
  \Leftrightarrow
  \pl F \kmarkwin2 \schFillIntGame{\kappa}
    \arrow[d] \\
  \pl F \ktactwin2 \schFillStrictGame{\kappa}
    \arrow[r] &
  \pl F \kmarkwin2\schFillGame{\kappa}
  \Leftrightarrow
  \pl F \kmarkwin2 \schFillInitialGame{\kappa}
      \arrow[d] \\
  &
  \pl F \kmarkwin2 \schFillStrictGame{\kappa}
\end{tikzcd}
\caption{Diagram of Scheeper/Menger game implications with \(\alcompS\kappa\)}
\label{GamesDiagram2}
\end{figure}

@@

\begin{proof}
  Since \(\alcompS\kappa\Rightarrow\pl F \ktactwin2\schFillStrictGame\kappa\) was
  a main result of \cite{MR1129143}, we need only show that
  \(\alcompS\kappa\Rightarrow \pl F \kmarkwin2\schFillIntGame\kappa\).

  Let \(f_A\) for \(A\in[\kappa]^{\leq\omega}\) witness \(\alcompS\kappa\). We define
  the \(2\)-mark \(\sigma\) as follows:
    \[
      \sigma(\<C\>,0) = \{\alpha\in C: f_C(\alpha) \leq 0 \}
    \]
    \[
      \sigma(\<C,D\>,n+1)
        =
      \{
        \alpha \in C\cap D
      :
        f_D(\alpha) \leq n+1 \text{ or }
        f_C(\alpha)\not=f_D(\alpha)
      \}
    .\]
  For any attack \(\<C_0,C_1,\dots\>\) by \(\pl C\) and
  \(\alpha\in\bigcap_{n<\omega}C_n\), either \(f_{C_n}(\alpha)\) is constant for
  all \(n\), or \(f_{C_n}(\alpha)\not=f_{C_{n+1}}(\alpha)\) for some \(n\);
  either way, \(\alpha\) is covered.
\end{proof}

\begin{corollary}
  \(\pl F \kmarkwin2\menGame{\onePtLind{\omega_1}}\).
\end{corollary}

@@

\begin{figure}[h]
\begin{tikzcd}[arrows=Rightarrow]
  \pl F \markwin \menGame{X}
    \arrow[r]
    \arrow[d,Leftrightarrow] &
  \pl F \kmarkwin2 \menGame{X}
    \arrow[r]
    \arrow[out=150,in=30,not,l]
    \arrow[d,Leftrightarrow] &
  \pl F \win \menGame{X}
    \arrow[r]
    \arrow[out=150,in=30,maybe,l]
    \arrow[d,Leftrightarrow] &
  \pl C \notwin \menGame{X}
    \arrow[out=150,in=30,not,l]
    \arrow[d,Leftrightarrow] \\
  \text{Markov Menger} &
  2\text{-Markov Menger} &
  \text{strategic Menger} &
  \text{Menger}
\end{tikzcd}
\caption{Diagram of covering properties related to the Menger game}
\label{menSpec}
\end{figure}

Limited information strategies for the Menger game naturally define the
spectrum of covering properties shown in Figure \ref{menSpec}. However,
we do not know if the middle two properties are actually distinct.

@@

We are also interested in non-game-theoretic characterizations of these
covering properties. It has been known for some time that metrizable strategic
Menger spaces are exactly the metrizable \(\sigma\)-compact spaces, shown first
by Telg\'arsky in \cite{MR753073} and later directly by Scheepers in
\cite{MR1273523}. It's Scheepers' technique which gives inspiration to
the following.

@@

  Let \(\mc U=\{U_y:y\in\text{cl}_X(Y)\}\) where each \(U_y\) is an open
  set in \(X\) containing \(y\); apply regularity to get
  \(y\in V_{y}\subseteq\text{cl}_X(V_{y})\subseteq U_{y}\)
  with \(V_{y}\) open in \(X\).
  Then \(\{X\setminus\text{cl}_X(Y)\}\cup\{V_{y}:y\in \text{cl}_X(Y)\}\)
  is an open cover of \(X\), so
  use relative compactness to choose a finite subset \(F\) of \(\text{cl}_X(Y)\)
  such that \(\{V_{y}:y\in F\}\) is a finite cover of \(Y\). Then since
  \(\bigcup\{\text{cl}_X(V_{y}):y\in F\}\) is a closed set in \(X\)
  containing \(Y\), it contains \(\text{cl}_X(Y)\), and thus
  \(\{U_{y}:y\in F\}\) is a finite subcollection of \(\mc U\) covering
  \(\text{cl}_X(Y)\).

@@

  We proceed by constructing basic open covers indexed by \(\omega^{<\omega}\)
  which will turn out to emulate the behavior of \(\pl C\) well enough
  that \(\pl F\) will be able to define a Markov strategy from a perfect
  information strategy by substituting
  these covers in the place of perfect information.
  So if \(\mc U_t\) is a basic open cover for \(t<s\in\omega^{<\omega}\), and
  \(\mc V\) is any basic open cover, we may choose a finite subcollection
  \(\mc F(s,\mc V)\) of \(\mc V\) such that
  \[
    \sigma(\<\mc U_{s\rest 1},\dots,\mc U_{s},\mc V\>)
      \subseteq
    \bigcup \mc F(s,\mc V)
  .\]

@@

\begin{proof}
  If \(X=\bigcup_{n<\omega}R_n\) for \(R_n\) relatively compact to \(X\),
  then for all \(\mc U\), let \(r_{\mc U}(x)\) be the
  least \(n\) such that \(x\in R_n\). Then \(c(\mc V,n)=\bigcup_{m\leq n}R_m\) and
  \(p(\mc U,\mc V,n+1) = \emptyset\).
\end{proof}

@@

We may also consider common counterexamples (specifically, examples
67 and 63 of \cite{MR1382863}) which are finer
than the usual Euclidean line.

@@

\begin{proof}
  Compact sets in \(R_{\mathbb Q}\) cannot contain open intervals,
  and thus are nowhere dense in nonmeager \(\mathbb R\),
  so \(R_{\mathbb Q}\) is not \(\sigma\)-compact. The usual base of
  intervals with rational endpoints (with or without rationals removed)
  witnesses second-countability.

  We now will show that \([-n,n]\setminus\mathbb Q\) is relatively compact.
  Let \(\mc U\) be a cover of
  \(R_{\mathbb Q}\) by open intervals with the rationals removed,
  and let \(\mc V\) be the corresponding cover of open intervals.
  There exists a finite subcollection of \(\mc V\) which covers
  \([-n,n]\), so there exists a corresponding subcollection of
  \(\mc U\) which covers \([-n,n]\setminus\mathbb Q\).
  Thus
  \(R_{\mathbb Q}=\mathbb Q\cup\bigcup_{n<\omega}([-n,n]\setminus\mathbb Q)\)
  is a countable union of relatively compact subsets.
\end{proof}

@@

\begin{lemma}\label{rOmegaLemma}
  For each compact subset \(K\) of \(\mathbb R\)
  and open cover \(\mc U\) of \(R_\omega\),
  there exists a countable set \(C\) such that \([a,b]\setminus C\)
  is \(\mc U\)-finite.
\end{lemma}

\begin{proof}
  Let \(\mc V\) be the corresponding open cover of \(\mathbb R\) where
  \(\mc U\) may be obtained by removing countable sets from members of
  \(\mc V\). Choose a finite subcollection \(\mc G\) of \(\mc V\) which
  covers \(K\), and then note that the corresponding finite subcollection
  \(\mc F\) of \(\mc U\) covers \([-n,n]\setminus C\) where \(C\) is the
  finite union of the countable sets removed from sets in \(\mc G\)
  to obtain the sets in \(\mc F\).
\end{proof}

@@

\begin{proof}
  If \(S\supseteq\{s_n:n<\omega\}\) for distinct \(s_n\),
  then \(U_m=R_\omega\setminus\{s_n:m<n<\omega\}\) yields an
  infinite cover \(\{U_m:m<\omega\}\) with no finite subcollection covering
  \(S\), showing that all relatively compact sets are finite, and \(R_\omega\)
  is not \(\sigma\)-relatively-compact. The set \(R_\omega\setminus\mathbb Q\)
  is open, but the closure of any open subset must contain a rational, so
  this space is not regular. Finally, the space is not second-countable,
  since for any countable collection of open sets \(\{U_n:n<\omega\}\),
  we may choose \(p_n\in U_n\)
  and note \(R_\omega\setminus\{p_n:n<\omega\}\) is an open set not containing
  any \(U_n\).

  Define the winning strategy \(\sigma\) for \(\pl F\) in
  \(\menGame{R_\omega}\) as follows: let
  \(\sigma(\<\mc{U}_0,\dots,\mc{U}_{2n}\>)=[-n,n]\setminus C_n\)
  where \(C_n\) witnesses Lemma \ref{rOmegaLemma} for \([-n,n]\)
  and \(\mc U_{2n}\),
  and let \(\sigma(\<\mc{U}_0,\dots,\mc{U}_{2n+1}\>)=\{c_{i,j} : i,j < n\}\).
\end{proof}

@@

\begin{proof}
  It's sufficient to show that \([0,1]\subseteq R_\omega\) is relatively
  robustly Menger. Let \(f_A\) witness \(\alcompS{\mf c}\)
  for \(A\in[[0,1]]^{\leq\omega}\).
  For each open cover \(\mc U\), let \(A_{\mc U}\) witness Lemma
  \ref{rOmegaLemma} for \([0,1]\) and \(\mc U\).
  Let \(r_{\mc U}(x)=0\) if \(x\in[0,1]\setminus A_{\mc U}\) and
  \(r_{\mc U}(x)=f_{\mc A_{\mc U}}(x)\) otherwise.
